Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-05-24 Paper.tex
Change 'positive' to 'non-negative' in some places.
Since 'positive', referred to numbers, typically means greater than 0, it may be
clearer to say 'non-negative'. This commit performs this replacement where
values in \mathbb{N} are mentioned.

There are still three remaining occurrences of 'positive', all in Appendix F,
which refer to EC private keys and coordinates of EC public keys.

Throughout, we assume scalars are positive integers and thus belong to the set $\mathbb{N}$. The set of all byte sequences is $\mathbb{B}$, formally defined in Appendix \ref{app:rlp}. If such a set of sequences is restricted to those of a particular length, it is denoted with a subscript, thus the set of all byte sequences of length $32$ is named $\mathbb{B}_{32}$ and the set of all positive integers smaller than $2^{256}$ is named $\mathbb{N}_{256}$. This is formally defined in section \hyperlink{block}{\ref{subsec:The_Block}}.

@@

\linkdest{R__u_assert}We assert $R_{\mathrm{u}}$, the cumulative gas used is a positive integer and that the logs Bloom, $R_{\mathrm{b}}$, is a hash of size 2048 bits (256 bytes):
\begin{equation}
R_{\mathrm{u}} \in \mathbb{N} \quad \wedge \quad R_{\mathrm{b}} \in \mathbb{B}_{256}
\end{equation}

@@

Thus $\mathtt{\tiny BE}$ is the function that expands a positive integer value to a big-endian byte array of minimal length and the dot operator performs sequence concatenation.

@@

If RLP is used to encode a scalar, defined only as a positive integer ($\mathbb{N}$ or any $x$ for $\mathbb{N}_{\mathrm{x}}$), it must be specified as the shortest byte array such that the big-endian interpretation of it is equal. Thus the RLP of some positive integer $i$ is defined as:
\begin{equation}
\mathtt{\tiny RLP}(i : i \in \mathbb{N}) \equiv \mathtt{\tiny RLP}(\mathtt{\tiny BE}(i))
\end{equation}

>>>>

Throughout, we assume scalars are non-negative integers and thus belong to the set $\mathbb{N}$. The set of all byte sequences is $\mathbb{B}$, formally defined in Appendix \ref{app:rlp}. If such a set of sequences is restricted to those of a particular length, it is denoted with a subscript, thus the set of all byte sequences of length $32$ is named $\mathbb{B}_{32}$ and the set of all non-negative integers smaller than $2^{256}$ is named $\mathbb{N}_{256}$. This is formally defined in section \hyperlink{block}{\ref{subsec:The_Block}}.

@@

\linkdest{R__u_assert}We assert $R_{\mathrm{u}}$, the cumulative gas used is a non-negative integer and that the logs Bloom, $R_{\mathrm{b}}$, is a hash of size 2048 bits (256 bytes):
\begin{equation}
R_{\mathrm{u}} \in \mathbb{N} \quad \wedge \quad R_{\mathrm{b}} \in \mathbb{B}_{256}
\end{equation}

@@

Thus $\mathtt{\tiny BE}$ is the function that expands a non-negative integer value to a big-endian byte array of minimal length and the dot operator performs sequence concatenation.

@@

If RLP is used to encode a scalar, defined only as a non-negative integer ($\mathbb{N}$ or any $x$ for $\mathbb{N}_{\mathrm{x}}$), it must be specified as the shortest byte array such that the big-endian interpretation of it is equal. Thus the RLP of some non-negative integer $i$ is defined as:
\begin{equation}
\mathtt{\tiny RLP}(i : i \in \mathbb{N}) \equiv \mathtt{\tiny RLP}(\mathtt{\tiny BE}(i))
\end{equation}
